### 2018-03-13 submission/supplemental.Rmd
pat updates
all pat's changes except fig adjustment and RF section

**Table S1: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Stool and Tissue**

@@

table_s1 <- temp_t1 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("brim", "zeller", "baxter", "hale"), 
                                      c("Brim", "Zeller", "Baxter", "Hale")), 
         comparison = "Adenoma", 
         sample_type = "Stool") %>% 
  select(fstat, r2, pvalue, study, comparison, sample_type)

@@

table_s2 <- temp_t2 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("wang", "weir", "ahn", "zeller", "baxter", "hale", "flemer"), 
                                      c("Wang", "Weir", "Ahn", "Zeller", "Baxter", "Hale", "Flemer")), 
         comparison = "Carcinoma", 
         sample_type = "Stool") %>% 
  select(fstat, r2, pvalue, study, comparison, sample_type)

@@

**Table S2: Alpha Diversity Metrics OR in Tissue**

**Table S3: OR in Stool of Tumor by Individual Genera with Initial P-Value under 0.05**

>>>>

**Table S1: Alpha Diversity Metrics OR in Tissue**

**Table S2: Bray-Curtis Distance Matrix Analyzed by PERMANOVA for Feces and Tissue**

@@

table_s1 <- temp_t1 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("brim", "zeller", "baxter", "hale"), 
                                      c("Brim", "Zeller", "Baxter", "Hale")), 
         comparison = "Adenoma", 
         sample_type = "Feces") %>% 
  select(fstat, r2, pvalue, study, comparison, sample_type)

@@

table_s2 <- temp_t2 %>% 
  mutate(fstat = round(fstat, digits = 2), 
         r2 = round(r2, digits = 3), 
         pvalue = round(pvalue, digits = 4), 
         study = stringr::str_replace(study, 
                                      c("wang", "weir", "ahn", "zeller", "baxter", "hale", "flemer"), 
                                      c("Wang", "Weir", "Ahn", "Zeller", "Baxter", "Hale", "Flemer")), 
         comparison = "Carcinoma", 
         sample_type = "Feces") %>% 
  select(fstat, r2, pvalue, study, comparison, sample_type)

@@

**Table S3: OR in Feces or Tumor by Individual Genera with Initial P-Value under 0.05**
